Value-Suppressing Uncertainty Maps

### 2017-03-18 paper/template.tex
Added methods notes from JH meeting

\title{Value-Suppressing Maps for Uncertain Data}

@@

	Uncertainty information is a vital part of many datasets, and should be accurately conveyed to the analyst.
	Directly integrating uncertainty information with data requires that designers construct bivariate maps that encode value and uncertainty simultaneously. The design of such bivariate maps can be difficult, and the impact of different choices of encodings on decision-making under uncertainty understudied.
    In this paper, we present a category of bivariate maps for uncertainty, ``value-suppressing maps.'' As opposed to traditional bivariate maps, value-suppressing maps make the informed decision to alias together values when uncertainty is high, in order to afford greater discriminability when uncertainty is low. That is, certain data is intrinsically easier to visually disambiguate than uncertain data. 
    We present several examples of these value-suppressing maps, as well as a crowd-sourced evaluation showing X. We conclude that Y.

@@

In this paper, we present \textbf{Value-Suppressing Maps} (VSMs) for integrating data and uncertainty information in thematic maps. VSMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a square bivariate map, with unique outputs for each relevant combination of data and uncertainty, VSMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain glyph regardless of their data value. Figure X shows an example of a VSM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSMs, examples of their utility for decision-making under uncertainty, and validate VDMs in a crowd-sourced experiment.

@@

% What this section needs to do
% State of the art in uncertainty vis, with heavy emphasis on MacEachren & co. 
% Bivariate maps are hard!
% Binning colormaps is de rigueur
% The variables we'd want to use for uncertainty (like value or alpha or size) mess with color discriminability

@@

\section{Value-Suppressing Maps}

@@

%Show:
% 1) Juxtaposition makes people ignore/underweight uncertainty (even when they don't screw up the search task)
% 2) VSMs make people, surprise surprise, bad at distinguishing highly uncertain values
% 3) But, they make uncertainty better-integrated
%    i) lower weights on uncertain values in decision-making
%    ii) a priori better discrimination

>>>>

\title{Value-Suppressing Uncertainty Maps}

@@

	Uncertainty information is a vital part of many datasets, and should be accurately conveyed to the analyst.
	Directly integrating uncertainty information with data requires that designers construct bivariate maps that encode value and uncertainty simultaneously. The design of such bivariate maps can be difficult, and the impact of different choices of encodings on decision-making under uncertainty understudied.
    In this paper, we present a category of bivariate maps for uncertainty, ``value-suppressing uncertainty maps,'' (VSUMS). As opposed to traditional bivariate maps, VSUMS make the informed decision to alias together values when uncertainty is high, in order to afford greater discriminability when uncertainty is low. That is, certain data is intrinsically easier to visually disambiguate than uncertain data. 
    We present several examples of these maps, as well as a crowd-sourced evaluation showing X. We conclude that Y.

@@

In this paper, we present \textbf{Value-Suppressing Uncertainty Maps} (VSUMs) for integrating data and uncertainty information in thematic maps. VSUMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a square bivariate map, with unique outputs for each relevant combination of data and uncertainty, VSUMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. Figure X shows an example of a VSUM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSUMs, examples of their utility for decision-making under uncertainty, and validate VSUMs in a crowd-sourced experiment.

@@

% What this section needs to do:
% State of the art in uncertainty vis, with heavy emphasis on MacEachren & co. 
% Bivariate maps are hard!
% Binning colormaps is de rigueur
% The variables we'd want to use for uncertainty (like value or alpha or size) mess with color discriminability

@@

\section{Value-Suppressing Uncertainty Maps}

@@

%Show:
% 1) Juxtaposition makes people ignore/underweight uncertainty (even when they don't screw up the search task)
% 2) VSUMs make people, surprise surprise, bad at distinguishing highly uncertain values
% 3) But, they make uncertainty better-integrated
%    i) lower weights on uncertain values in decision-making
%    ii) a priori better discrimination
